\gettitle

### 2019-11-14 assignment2/submission2.tex
Fix errors and formatting in submission2

\begin{table}[!htb]
	\begin{minipage}[t]{.33\linewidth}
		\centering
			\begin{tabular}{|l|l|}
				\hline
				1 & 11 \\ \hline
				2 & 11 \\ \hline
				3 & 11 \\ \hline
				4 & 16 \\ \hline
				5 & 23 \\ \hline
			\end{tabular}
		\caption{4}
	\end{minipage}%
	\hfill%
	\begin{minipage}[t]{.33\linewidth}
		\centering
		\begin{tabular}{|l|l|}
			\hline
			1 & 16 \\ \hline
			2 & 16 \\ \hline
			3 & 16 \\ \hline
			4 & 19 \\ \hline
			5 & 31 \\ \hline
		\end{tabular}
		\caption{11}
	\end{minipage}%
	\hfill%
	\begin{minipage}[t]{.33\linewidth}
		\centering
		\begin{tabular}{|l|l|}
			\hline
			1 & 4 \\ \hline
			2 & 26 \\ \hline
			3 & 23 \\ \hline
			4 & 19 \\ \hline
			5 & 19 \\ \hline
		\end{tabular}
		\caption{16}
\end{minipage}
\end{table}

\begin{table}[!htb]
	\begin{minipage}[t]{.33\linewidth}
		\centering
		\begin{tabular}{|l|l|}
			\hline
			1 & 23 \\ \hline
			2 & 23 \\ \hline
			3 & 23 \\ \hline
			4 & 31 \\ \hline
			5 & 4 \\ \hline
		\end{tabular}
		\caption{19}
	\end{minipage}%
	\hfill%
	\begin{minipage}[t]{.33\linewidth}
		\centering
		\begin{tabular}{|l|l|}
			\hline
			1 & 26 \\ \hline
			2 & 26 \\ \hline
			3 & 31 \\ \hline
			4 & 31 \\ \hline
			5 & 11 \\ \hline
		\end{tabular}
		\caption{23}
	\end{minipage}%
	\hfill%
	\begin{minipage}[t]{.33\linewidth}
		\centering
		\begin{tabular}{|l|l|}
			\hline
			1 & 31 \\ \hline
			2 & 31 \\ \hline
			3 & 31 \\ \hline
			4 & 4 \\ \hline
			5 & 11 \\ \hline
		\end{tabular}
		\caption{26}
	\end{minipage}
\end{table}

\begin{table}[!ht]
	\centering
	\begin{tabular}{|l|l|}
		\hline
		1 & 4 \\ \hline
		2 & 4 \\ \hline
		3 & 4 \\ \hline
		4 & 11 \\ \hline
		5 & 16 \\ \hline
	\end{tabular}
	\caption{31}
\end{table}
\subsection*{b)}
\begin{enumerate}
	\item node 4 $ \rightarrow $ node 16
	\item node 16 $ \rightarrow $ node 19
	\item node 19 $ \rightarrow $ node 23
\end{enumerate}
\subsection*{c)}
\begin{table}[!ht]
	\centering
	\begin{tabular}{|l|l|}
		\hline
		1 & 26 \\ \hline
		2 & 26 \\ \hline
		3 & 31 \\ \hline
		4 & 4 \\ \hline
		5 & 11 \\ \hline
	\end{tabular}
	\caption{24}
\end{table}
The finger tables of Node 11, 16, 19 and 23 should be recomputed.\\
The changes only occur in Node 16 and 23.
\subsection*{d)}
Looking at the node 23, there has to be an update on the fifth entry on the finger table. When Node 7 and 9 are joining at the exact same time the fifth entry on the finger table of node 23 can become invalid. Same applies for Node 31 in the fourth entry.
\subsection*{e)}
\subsection*{f)}

\section*{3 - Name Services}
\subsection*{a)}
\begin{table}[!ht]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		& Iterative resolution & Recursive resolution \\ \hline
		1. Lookup & 5 & 5 \\ \hline
		2. Lookup & 5 & 5 \\ \hline
		3. Lookup & 5 & 5 \\ \hline
	\end{tabular}
\end{table}
\subsection*{b)}
\begin{table}[!ht]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		& Iterative resolution & Recursive resolution \\ \hline
		1. Lookup & 5 & 5 \\ \hline
		2. Lookup & 5 & 4 \\ \hline
		3. Lookup & 5 & 5 \\ \hline
	\end{tabular}
\end{table}
\subsection*{c)}

>>>>

	\begin{minipage}[t]{.25\linewidth}
        \centering
        Node 4:\\
			\begin{tabular}{|l|l|}
				\hline
				1 & 11 \\ \hline
				2 & 11 \\ \hline
				3 & 11 \\ \hline
				4 & 16 \\ \hline
				5 & 23 \\ \hline
			\end{tabular}
	\end{minipage}%
	\begin{minipage}[t]{.25\linewidth}
        \centering
        Node 11:\\
		\begin{tabular}{|l|l|}
			\hline
			1 & 16 \\ \hline
			2 & 16 \\ \hline
			3 & 16 \\ \hline
			4 & 19 \\ \hline
			5 & 31 \\ \hline
		\end{tabular}
	\end{minipage}%
	\begin{minipage}[t]{.25\linewidth}
        \centering
        Node 16:\\
		\begin{tabular}{|l|l|}
			\hline
			1 & 19 \\ \hline
			2 & 19 \\ \hline
			3 & 23 \\ \hline
			4 & 26 \\ \hline
			5 & 4 \\ \hline
		\end{tabular}
    \end{minipage}
    \begin{minipage}[t]{.25\linewidth}
        \centering
        Node 19:\\
        \begin{tabular}{|l|l|}
            \hline
            1 & 23 \\ \hline
            2 & 23 \\ \hline
            3 & 23 \\ \hline
            4 & 31 \\ \hline
            5 & 4 \\ \hline
        \end{tabular}
    \end{minipage}%

	\begin{minipage}[t]{.25\linewidth}
		\centering
        Node 23:\\
		\begin{tabular}{|l|l|}
			\hline
			1 & 26 \\ \hline
			2 & 26 \\ \hline
			3 & 31 \\ \hline
			4 & 31 \\ \hline
			5 & 11 \\ \hline
		\end{tabular}
	\end{minipage}%
	\begin{minipage}[t]{.25\linewidth}
		\centering
        Node 26:\\
		\begin{tabular}{|l|l|}
			\hline
			1 & 31 \\ \hline
			2 & 31 \\ \hline
			3 & 31 \\ \hline
			4 & 4 \\ \hline
			5 & 11 \\ \hline
		\end{tabular}
	\end{minipage}
	\begin{minipage}[t]{.25\linewidth}
		\centering
        Node 31:\\
		\begin{tabular}{|l|l|}
			\hline
			1 & 4 \\ \hline
			2 & 4 \\ \hline
			3 & 4 \\ \hline
			4 & 11 \\ \hline
			5 & 16 \\ \hline
		\end{tabular}
	\end{minipage}

\subsection*{b)}
\begin{enumerate}
	\item node 4 $ \rightarrow $ node 16
	\item node 16 $ \rightarrow $ node 19
	\item node 19 $ \rightarrow $ node 23
\end{enumerate}

\subsection*{c)}
\begin{minipage}[t]{.25\linewidth}
	\centering
    Node 24:\\
	\begin{tabular}{|l|l|}
		\hline
		1 & 26 \\ \hline
		2 & 26 \\ \hline
		3 & 31 \\ \hline
		4 & 4 \\ \hline
		5 & 11 \\ \hline
	\end{tabular}
\end{minipage}

The finger table of node 16 will change eventually while the one for node 23 will change immediately.

\subsection*{d)}
If both nodes join simultaneously they are between the same two nodes (4 and 11). If they now try to each update their predecessor and successor then we have a race condition while updating a linked list. This can leave the list (or in this case ring) in an inconsistent state that makes routing impossible!

\subsection*{e)}
\subsection*{f)}

\section*{3 - Name Services}

\subsection*{a)}
\begin{center}
	\begin{tabular}{|c|c|c|}
		\hline
		& Iterative resolution & Recursive resolution \\ \hline
		1. Lookup & 10 & 10 \\ \hline
		2. Lookup & 10 & 10 \\ \hline
		3. Lookup & 8 & 8 \\ \hline
	\end{tabular}
\end{center}

\subsection*{b)}
\begin{center}
	\begin{tabular}{|c|c|c|}
		\hline
		& Iterative resolution & Recursive resolution \\ \hline
		1. Lookup & 10 & 10 (8 fast, 2 slow) \\ \hline
		2. Lookup & 10 & 8 (6 fast, 2 slow) \\ \hline
		3. Lookup & 8 & 8 (6 fast, 2 slow) \\ \hline
	\end{tabular}
\end{center}
